Topological Equivariant Artist Model for Visualization Library Architecture

### 2025-01-03 paper/main.tex
typo

In \autoref{fig:artist:xi} each orange band is defined as $\frac{7\pi}{4}\times [0,1]$ such that each point on each band maps to the same point $\vindex|_{\frac{7\pi}{4}\times [0,1]} = \frac{7\pi}{2}$. As illustrated in \autoref{fig:atct:morphisms:sheaf}, each band acts as an indexer into its corresponding image because the section \gsection\ takes as input coordinates $(\frac{7\pi}{2}, \beta), \beta \in [0,1]$ in each orange band and returns the settings for the pixel it maps into. As illustrated in \autoref{fig:artist:xi}, the definition of $\vindex$ allows for some flexibility in the shape of $\gbase$. An annulus $\gbase_0$ is used for the green circle in \autoref{fig:atct:morphisms:sheaf} because that cyclical structure is in the graphic and in \dbase\, but rectangles $\gbase_1, \gbase_2$ are used for the $\sin$ and $\cos$ curves because they are linear. Despite discarding the cyclical information embedded in \dbase\, the spaces $\gbase_1$ and $\gbase_2$ are structure preserving because they satisfy the constraint on \vindex\ that every graphic element maps back into a data element \cite{ziemkiewiczEmbeddingInformationVisualization2009}.

@@

\note{stop here}
\subsection{Equivariance}
\label{sec:artist:equiv}
As introduced in \autoref{sec:related-work:equivariance}, data and the corresponding visual encoding are expected to have compatible structure. This structure can be formally expressed as actions $\dfunc \in \dfuncset$ on the sheaf $\sheaf_{\dbase, \dtotal}$. We generalize from binary operations to a family of actions because that allows for expanding the set of allowable transformations on the data beyond a single operator. We describe the changes on the graphic side as changes in measurements \measure\, which are scaler or vector components of the rendered graphic that can be quantified, such as the color, position, shape, texture, or rotation angle of the graphic. The visual variables \cite{bertinIIPropertiesGraphic2011} are a subset of measurable components. For example, a measurement of a scatter marker could be its color (e.g. red) or its x position (e.g. 5).

>>>>

In \autoref{fig:artist:xi} each orange band is defined as $\frac{7\pi}{4}\times [0,1]$ such that each point on each band maps to the same point $\vindex|_{\frac{7\pi}{4}\times [0,1]} = \frac{7\pi}{2}$. As illustrated in \autoref{fig:atct:morphisms:sheaf}, each band acts as an indexer into its corresponding image because the section \gsection\ takes as input coordinates $(\frac{7\pi}{4}, \beta), \beta \in [0,1]$ in each orange band and returns the settings for the pixel it maps into. As illustrated in \autoref{fig:artist:xi}, the definition of $\vindex$ allows for some flexibility in the shape of $\gbase$. An annulus $\gbase_0$ is used for the green circle in \autoref{fig:atct:morphisms:sheaf} because that cyclical structure is in the graphic and in \dbase\, but rectangles $\gbase_1, \gbase_2$ are used for the $\sin$ and $\cos$ curves because they are linear. Despite discarding the cyclical information embedded in \dbase\, the spaces $\gbase_1$ and $\gbase_2$ are structure preserving because they satisfy the constraint on \vindex\ that every graphic element maps back into a data element \cite{ziemkiewiczEmbeddingInformationVisualization2009}.

@@

\subsection{Equivariance}
\label{sec:artist:equiv}
As introduced in \autoref{sec:related-work:equivariance}, data and the corresponding visual encoding are expected to have compatible structure. This structure can be formally expressed as actions $\dfunc \in \dfuncset$ on the sheaf $\sheaf_{\dbase, \dtotal}$. We generalize from binary operations to a family of actions because that allows for expanding the set of allowable transformations on the data beyond a single operator. We describe the changes on the graphic side as changes in measurements \measure\, which are scaler or vector components of the rendered graphic that can be quantified, such as the color, position, shape, texture, or rotation angle of the graphic. The visual variables \cite{bertinIIPropertiesGraphic2011} are a subset of measurable components. For example, a measurement of a scatter marker could be its color (e.g. red) or its x position (e.g. 5).
